### Links

```{r echo=FALSE}
source("R/common.R")
source("R/latex.R")
LoadPackage("tidyverse")
LoadPackage("kableExtra")
```

#### General Properties

The data columns are following this pattern: `<Relation>_<Metric>`,  for example `CC_RTD`, which describes that the cloud layer uses, requires, or obtains the Round-trip delay (RTD).

Relations:

- `CC`: Between cloud nodes
- `CF`: Between cloud and fog nodes
- `CE`: Between cloud and edge nodes
- `CU`: Between cloud and end users
- `FF`: Between fog nodes
- `FE`: Between fog and edge nodes
- `FU`: Between fog and end users
- `EE`: Between edge nodes
- `EU`: Between edge nodes and end users
- `UU`: Between end users

All relations can indicate both directions equivalently, for example, `CF` means cloud-to-fog and fog-to-cloud interactions. 

Metrics are listed below.

#### Round-trip delay Properties

Metrics:

- `RTD`: Round-trip delay

Additional columns:

- `RTD_MEASURING_STATIC`: Indicates how the RTD is obtained.
  - `y`: Means "yes", RTD is used, required, or obtained in a static way. It does not change over time.
  - `n`: Means "no" usage of RTD.
- `RTD_MEASURING_DYNAMIC`: Indicates how the RTD is obtained.
  - `y`: Means "yes", RTD is used, required, or obtained in a dynamic way. It does change over time.
  - `n`: Means "no" usage of RTD. 

```{r}
linksRTDProps <- read.csv2("csv/links-round-trip-delay-properties.csv")
```

#### End-to-end delay Properties

Metrics:

- `E2E`: End-to-end delay

Additional columns:

- `E2E_MEASURING_STATIC`: Indicates how the E2E is obtained.
  - `y`: Means "yes", E2E is used, required, or obtained in a static way. It does not change over time.
  - `n`: Means "no" usage of E2E
- `E2E_MEASURING_DYNAMIC`: Indicates how the E2E is obtained.
  - `y`: Means "yes", E2E is used, required, or obtained in a dynamic way. It does change over time.
  - `n`: Means "no" usage of E2E. 

```{r}
linksE2EProps <- read.csv2("csv/links-end-to-end-delay-properties.csv")
```

#### Bandwidth Properties

Metrics:

- `BW`: Bandwidth

Additional columns:

- `BW_MEASURING_STATIC`: Indicates how the BW is obtained.
  - `y`: Means "static", BW is used, required, or obtained in a static way. It does not change over time.
  - `n`: Means "no" usage of BW.
- `BW_MEASURING_DYNAMIC`: Indicates how the BW is obtained.
  - `y`: Means "dynamic", BW is used, required, or obtained in a dynamic way. It does change over time.
  - `n`: Means "no" usage of BW. 

```{r}
linksBWProps <- read.csv2("csv/links-bandwidth-properties.csv")
```

#### Hop Properties

```{r}
# hop properties

```
