# Nodes

## Required Libraries

```{r warning=FALSE}
if(!require(kableExtra)){
    install.packages("kableExtra")
    library(kableExtra)
}
if(!require(tidyverse)){
    install.packages("tidyverse")
    library(tidyverse)
}
```

## Functions

Important symbols:

- `y`: Means "yes", in terms of used or required. 
- `n`: Means "no", in terms of **not** used or **not** required.
- `#`: Means that number of logical CPU cores is required.
- `~`: Means not further specified. Is is used, when particular requirement are mentioned, but not further specified.
- `*`: Means multiple occurrences. For example, it is used when multiple fog layers or edge layers are used.

```{r}
ReplaceSymbol <- function(symbol) {
  switch(symbol,
         "y" = "\\\\ding{51}",
         "x" = "\\\\ding{55}",
         "#" = "\\\\#",
         "~" = "\\\\ding{109}",
         "*" = "\\ding{81}"
         )
}

ReplaceSymbolsInCols<- function(df) {
  return (df %>% 
  mutate_all(., funs(gsub('#', ReplaceSymbol("#"),. , fixed = FALSE))) %>% 
  mutate_all(., funs(gsub('\\by\\b', ReplaceSymbol("y"),. , fixed = FALSE))) %>% 
  mutate_all(., funs(gsub('\\b~\\b', ReplaceSymbol("~"),. , fixed = FALSE))) %>% 
  mutate_all(., funs(gsub('\\bx\\b', ReplaceSymbol("x"),. , fixed = FALSE))) %>% 
  mutate_all(., funs(gsub('*', ReplaceSymbol("*"),. , fixed = TRUE))))
}
```

## Read CSVs

```{r}
sProps <- read.csv2("csv/nodes-static-properties.csv")
dProps<- read.csv2("csv/nodes-dynamic-properties.csv")
```

## Replace Symbols in Columns

```{r warning=FALSE}
sPropsMutated <- ReplaceSymbolsInCols(sProps)
dPropsMutated <- ReplaceSymbolsInCols(dProps)
```

## Create LaTeX Table

### Dynamic Node Properties

```{r}
kbl_fn_footnote_as_chunk = TRUE
kbl_fn_threeparttable = TRUE
kbl_fn_general_title = ""

sPropsKblCaption <- "Obtained Static Node Properties"

sPropsKbl <- kbl(sPropsMutated, "latex", escape = FALSE, caption = sPropsKblCaption, booktabs = TRUE) %>% 
  kable_styling(latex_options = "scale_down") %>%
  footnote(., general = c("C: Cloud, F: Fog, E: Edge, G: Gateway, CPU: Central Processing Unit, Mem: Memory, Disk: Storage, Net: Network"), general_title = kbl_fn_general_title, footnote_as_chunk = kbl_fn_footnote_as_chunk, threeparttable = kbl_fn_threeparttable)

save_kable(sPropsKbl, "latex/nodes-static-properties.tex")
```

### Static Node Properties

```{r}
dPropsKblCaption <- "Obtained Dynamic Node Properties"

dPropsKbl <- kbl(dPropsMutated, "latex", escape = FALSE, caption = dPropsKblCaption, booktabs = TRUE) %>% 
  kable_styling(latex_options = "scale_down") %>%
  footnote(., general = c("C: Cloud, F: Fog, E: Edge, G: Gateway, CPU: Central Processing Unit, Mem: Memory, Disk: Storage, Net: Network"), general_title = kbl_fn_general_title, footnote_as_chunk = kbl_fn_footnote_as_chunk, threeparttable = kbl_fn_threeparttable)

save_kable(dPropsKbl, "latex/nodes-dynamic-properties.tex")
```
