### Nodes

```{r echo=FALSE, message=FALSE, warning=FALSE}
source("R/common.R")
source("R/latex.R")
source("R/kable.R")
LoadPackage("tidyverse")
LoadPackage("kableExtra")
LoadPackage("ggpubr")
LoadPackage("ggplot2")
```

#### Static Properties

Properties:

- `Cloud`: If nodes of type cloud are required.
- `Fog`: If nodes of type fog are required.
- `Edge`: If nodes of type edge are required.
- `Gateway`: If nodes of type gateway are required.
- `Layer`: Specifies that nodes are assigned a layer number. This is required, for example, when layers are further horizontally partitioned. Example: There is a fog layer 1 and are fog layer 2.
- `Role`: Specifies that nodes are assigned a particular role. Example: There are fog control nodes.
- `Location_Place`: The location of a particular node is required. Example: A node is located in "Frankfurt, Germany".
- `Location_GPS`: The GPS coordinates of a particular node are required. Example: The GPS coordinates are described with longitude and latitude.
- `Group`: It is required to group nodes, for example, nodes in a particular region are grouped logically.
- `CPU_MIPS`: The CPU capabilities are required in MIPS. Example: 1000 MIPS.
- `CPU_Cores`: The CPU capabilities in number of cores are required. Example: 8 cores.
- `CPU_Threads`: The CPU capabilities in number of threads are required. Example: 16 cores.
- `CPU_GFlop`: The CPU capabilities in GFlop are required.
- `CPU_Frequency`: The CPU capabilities in terms of frequency are required. Example: 2.0 GHz.
- `CPU_Shares`: The CPU capabilities in shares are required. Example: 1000m.
- `CPU_Slots`: The CPU capabilities in terms of slots are required. Example: 10 Slots are available. This value is normally calculated out of other values.
- `Memory_Capacity`: The available memory is required in MB, GB, or TB. Example: 5 GB.
- `Memory_Slots`: The memory resources in terms of slots are required. Example: 10 Slots are available. This value is normally calculated out of other values.
- `Disk_Capacity`: The available disk space is required in MB, GB, or TB. Example: 500 GB.
- `Disk_Slots`: The available disk space in terms of slots is required. Example: 10 Slots are available. This value is normally calculated out of other values.
- `Network_Capacity`: The available network resources are required. This is usually the available bandwidth provided by the network interfaces of a particular node. Example: 1000 Mbps download/upload.

```{r}
nodesStaticProps <- read.csv2("csv/nodes-static-properties.csv")
```

```{r echo=FALSE}
CreateScrollableTable(nodesStaticProps)
```

#### Dynamic Properties

Properties:

- `CPU_Util`: Represents the current CPU utilization. Example: 0.95.
- `Memory_Util`: Represents the current memory utilization. Example: 0.40.
- `Disk_Util`: Represents the current disk utilization in terms of used storage. Example: 0.35. This is **not** I/O utilization.
- `Network_Tx`: Amount of transmitted traffic via the network interface. Example: 1500 byte.
- `Network_Rx`: Amount of received traffic via the network interfaces. Example: 1800 byte.
- `Energy`: Consumed energy by the node. Example: 1500 J. Different values are possible based on custom calculation steps proposed by various authors.
- `Costs`: Costs for running the node, usually expressed in $.
- `Workloads`: List of allocated workloads on a particular node.

```{r}
nodesDynamicProps<- read.csv2("csv/nodes-dynamic-properties.csv")
```
