---
title: "PULCEO: Structured Literature Review Source Repository"
knit: (function(input_file, encoding) {
  out_dir <- '../docs';
  rmarkdown::render(input_file,
  encoding=encoding,
  output_file=file.path(dirname(input_file), out_dir, "index.html"))})
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

<h1><span style="color:red"> +++ Attention +++ This is still work-in-progress and is thus subject to change +++</span></h1>

# Resources

All resources with their required attributes are stored in CSV files.

The first three columns of all CSV are the following:

- `ID`: Identifies a particular paper, type `Integer`. 
- `Author`: The author(s) of a particular paper, type `String`.
- `Year`: The year of the publication, type `Integer`.

All other columns follow the pattern `<Attribute>` (Example: `Location`) or `<Attribute>_<Specialization>` (Example: `Location_GPS`).

Only two characteristics attributes are possible:

- `y`: Means "yes", in terms of **used** or **required**.
- `n`: Means "no", in terms of **not used** or **not required**.

```{r child=c('nodes.Rmd')}
```

```{r child=c('links.Rmd')}
```

The following resources are not covered so far:

- Groups
- Workloads
- Paths
- Requests
- Users

```{r child=c('references.Rmd')}
```